\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2021-12-04 main.Rmd
a croase draft for the interactive graphic section

Interactive graphics give users the chance to manipulate the graphes for additional information. This is especially useful for spatio-temporal data since it would be interesting to explore the correlation between nearby sites on the map or compare between clusters. Underlying each interactive graphic system is a pipeline workflow that communicates the user action down the workflow to [...]. Various such workflow has been proposed in the 90s literature, including [...]. Current general purpose R implementation on iterative graphics includes: plotly [@plotly] for [...]; ggiraph [@ggiraph] for [...]; crosstalk[@crosstalk] for [...]. Specifically for spatio-temporal data, there is tmap [@map], leftlet [@leaflet], mapview [@mapview].

some common interactive actions include zoom and panning, tooltip/ highlight, and more advanced cross-linking.

@@

>>>>

Interactive graphics give users the chance to manipulate the graphes for additional information. This is especially useful for spatio-temporal data since users can zoom or pan the map to see different areas; use tooltips or popups to query more detailed information about a particular point; or explore points in multiple facets through highlight and cross-linking.

Current general purpose R implementation on iterative graphics includes: plotly [@plotly], leaflet [@leaflet], and mapdeck [@mapdeck] uses the underlying javascript library plotly.js, leaflet.js, and mapbox.js; ggiraph [@ggiraph] for [...]; crosstalk [@crosstalk] has developed a cross linking between html widgets. There's also more R implement that produces leaflet extension, i.e. tmap [@map], mapview [@mapview], leafpop [@leafpop], and leafgl [@leafgl].

Underlying each interactive graphic system is a pipeline workflow that communicates the user action down the workflow to [...]. Various such workflow has been proposed in the 90s literature, including [...]. These designs do the linking as follows: when an user action is captured, the system searches for the unique identifiers of that observation, and fetches the queried information with the same unique identifiers.

With spatial temporal data, a common type of user action is to link between the time series plotted with the site on the map. Figure \ref{fig:interactive-workflow} shows how does interactivities work with graphics created by two forms in a cubble.  With cubble, the time series plot and site map can be created with the long and nested form separately. The unique identifier shared by both the nested and long form in a cubble is the `key` variable. Once a user action is captured, the system will look for the corresponding key variable, which will highlight the observations in both forms. Then graphics will be updated with the highlighted observations.

@@

```{r echo = FALSE, out.width="50%", out.height="30%"}
knitr::include_graphics(here::here("figures/popup.png"))
```

### 2021-12-04 main.tex
a croase draft for the interactive graphic section

@@

>>>>

Interactive graphics give users the chance to manipulate the graphes for
additional information. This is especially useful for spatio-temporal
data since users can zoom or pan the map to see different areas; use
tooltips or popups to query more detailed information about a particular
point; or explore points in multiple facets through highlight and
cross-linking.

Current general purpose R implementation on iterative graphics includes:
plotly \citep{plotly}, leaflet \citep{leaflet}, and mapdeck
\citep{mapdeck} uses the underlying javascript library plotly.js,
leaflet.js, and mapbox.js; ggiraph \citep{ggiraph} for {[}\ldots{]};
crosstalk \citep{crosstalk} has developed a cross linking between html
widgets. There's also more R implement that produces leaflet extension,
i.e.~tmap \citep{map}, mapview \citep{mapview}, leafpop \citep{leafpop},
and leafgl \citep{leafgl}.

Underlying each interactive graphic system is a pipeline workflow that
communicates the user action down the workflow to {[}\ldots{]}. Various
such workflow has been proposed in the 90s literature, including
{[}\ldots{]}. These designs do the linking as follows: when an user
action is captured, the system searches for the unique identifiers of
that observation, and fetches the queried information with the same
unique identifiers.

With spatial temporal data, a common type of user action is to link
between the time series plotted with the site on the map. Figure
\ref{fig:interactive-workflow} shows how does interactivities work with
graphics created by two forms in a cubble. With cubble, the time series
plot and site map can be created with the long and nested form
separately. The unique identifier shared by both the nested and long
form in a cubble is the \texttt{key} variable. Once a user action is
captured, the system will look for the corresponding key variable, which
will highlight the observations in both forms. Then graphics will be
updated with the highlighted observations.

@@

\begin{center}\includegraphics[width=0.5\linewidth,height=0.3\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/popup} \end{center}
